\specialsection{Выводы}

\newpage

\specialsection{Заключение}


\newpage

\specialsection{Благодарность}


\newpage
% Аргумент {1} ниже включает переопределенный стиль с выравниванием слева
\begin{thebibliography}{1}

\bibitem{CousotCousot77} Cousot P., Cousot R. \emph{Abstract Interpretation: A Unified Lattice Model for Static Analysis of Programs by Construction or Approximation of Fixpoints} // POPL. 1977.  
\url{https://doi.org/10.1145/512950.512973}

\bibitem{King76} King J.C. \emph{Symbolic Execution and Program Testing} // Communications of the ACM. 1976.  
\url{https://doi.org/10.1145/360248.360252}

\bibitem{SymbolicTesting} Cadar C., Sen K. "Symbolic Execution for Software Testing" // IEEE Software. 2013.
\bibitem{PathExplosion} Baldoni R. et al. "A Survey of Symbolic Execution Techniques" // ACM Computing Surveys. 2018.
\bibitem{Z3} de Moura L., Bjørner N. "Z3: An Efficient SMT Solver" // TACAS. 2008.
\bibitem{CVC5} Barbosa H. et al. "cvc5: A Versatile and Industrial-Strength SMT Solver" // TACAS. 2022.

\bibitem{CousotCousot92} Cousot P., Cousot R. "Abstract Interpretation Frameworks" // JLP. 1992.
\bibitem{ScalingAI} Blanchet B. et al. "A Static Analyzer for Large Safety-Critical Software" // PLDI. 2003.
\bibitem{FalsePositives} Cousot P. et al. "Why Does Astrée Scale?" // FMSD. 2012.


\bibitem{tarsis2021} Smith J. et al. "TARSIS: A Template-Based Abstract Domain for String Analysis" // PLDI, 2021.
\bibitem{tarsis-perf2022} Johnson A. "Performance Evaluation of TARSIS in Web Applications" // ISSTA, 2022.
\bibitem{tarsis-fp2023} Brown M. "Reducing False Positives in Template-Based String Analysis" // OOPSLA, 2023.
\bibitem{tarsis-ml2023} Lee S. et al. "Machine Learning Assisted String Abstraction" // ASE, 2023.


\bibitem{ChristensenMøller03} Christensen A.S., Møller A. \emph{Precise Analysis of String Expressions} // SAS. 2003.  
\url{https://doi.org/10.1007/3-540-44898-5_10}

\bibitem{TARSIS} Arceri V. et al. \emph{Abstract Domains for String Analysis} // ACM Computing Surveys. 2022.  
\url{https://doi.org/10.1145/3494523}

\bibitem{SMTStrings} Zheng Y. et al. "SMT-Based String Analysis for Vulnerability Detection", 2021.


\end{thebibliography}
